\chapter{Abstract}

%This is for reference only. Delete before finalization
\begin{Justify}
    
\end{Justify}
\noindent This chapter sets the stage for the project titled "House Price Prediction Models" by diving into its background, purpose, goals, and what it aims to achieve. It explores the key ideas behind the project, explains why it’s important in real estate analytics, and pinpoints the problem it’s tackling. The chapter also discusses why the proposed solution is practical, uncovers weaknesses in current approaches, and gives a clear picture of the expected results from the project.
\end{center}
%This is for reference only. Delete before finalization


% Start sections and sub-sections
\begin{Justify}
    
\section{Abstract}

House price prediction has been a core area of research in real estate analytics, urban planning, and financial forecasting. With increasing urbanization, dynamic socio-economic factors, and the growing need for accurate property valuation, predictive modeling of house prices has gained immense importance. Traditional regression techniques often fail to capture complex non-linear relationships and multi-dimensional influences on property values.

In this project, we aim to predict house prices at the subregion level by leveraging machine learning techniques, specifically deep neural networks. Our work is inspired by the research paper titled ``Joint Gated Co-Attention Based Multi-Modal Networks for Subregion House Price Prediction,'' which proposed an advanced architecture involving multiple feature integration methods.

Given the complexity of the original model, we implemented a simplified approach using fully connected neural networks, focusing on the core objective of achieving acceptable predictive performance while establishing a foundation for future enhancement with more sophisticated architectures like attention mechanisms and multi-branch networks.


